Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-15 writeups/dissertation/dissertation.tex
foo

\begin{table}[!ht]
  \caption{Base-level component of ACT-R declarative memory}
  \label{tabACTRBLLModel}
  {\tabulinesep=1.2mm
    \begin{tabu}{ll}
      \hline
      Common Name &  Equation \\
      \hline
      Base Level Activation &	$B_{i} = log \sum_{j=1}^{n} {t_{j}}^{-d}$ \\
      Optimized Learning &	$B_{i} = log \frac{n}{1-d} - d * log L$
      \hline
    \end{tabu}
  }
\end{table}

@@

The base-level ($B_{i}$) component in Table \ref{ACTRBLLModel} is different than the $B_{i}$ used in \textcite{Stanley2013} (Table \ref{ModACTRModel}).
\authorcite{Stanley2013} assumed no time dependence, no decay rate, and that the $B_{i}$ is simply a log odds computation of the probability that each chunk is likely to be presented again, given past frequency.
If a decay rate of 0 is used on the optimized learning form of $B_{i}$, then the equation collapses to $log n_{i}$,
which is a nonlinear transformation of the $B_{i}$ used by \authorcite{Stanley2013} ($log \frac{p_{i}}{1-p_{i}}$).
Both forms maintain the same rank ordering, so they should produce similar results.
So the $B_{i}$ component used by \authorcite{Stanley2013} can be roughly thought of as the standard form of $B_{i}$ when the decay rate is 0 (i.e., a pure frequency model).

>>>>

\begin{table}[!ht]
  \caption{Base-level component of ACT-R declarative memory}
  \label{tabACTRBLLModel}
  {\tabulinesep=1.2mm
    \begin{tabu}{ll}
      \hline
      Common Name &  Equation \\
      \hline
      Base Level Activation &	$B_{i} = log \sum_{j=1}^{n} {t_{j}}^{-d}$ \\
      Optimized Learning &	$B_{i} = log \frac{n}{1-d} - d * log L$ \\
      \hline
    \end{tabu}
  }
\end{table}

@@

The base-level ($B_{i}$) component in Table \ref{ACTRBLLModel} is different than the $B_{i}$ used in \textcite{Stanley2013} (Table \ref{ModACTRModel}).
\citeauthor{Stanley2013} assumed no time dependence, no decay rate, and that the $B_{i}$ is simply a log odds computation of the probability that each chunk is likely to be presented again, given past frequency.
If a decay rate of 0 is used on the optimized learning form of $B_{i}$, then the equation collapses to $log n_{i}$,
which is a nonlinear transformation of the $B_{i}$ used by \citeauthor{Stanley2013} ($log \frac{p_{i}}{1-p_{i}}$).
Both forms maintain the same rank ordering, so they should produce similar results.
So the $B_{i}$ component used by \citeauthor{Stanley2013} can be roughly thought of as the standard form of $B_{i}$ when the decay rate is 0 (i.e., a pure frequency model).
